% This is a thesis template that attempts to conform to the guidelines
% published by UTRGV's Graduate School office.

% Please report any issues to
% https://github.com/UTRGV-SMSS/Thesis-Template/issues

% The author of this template is Guillermo Garza.
% Modified by Moises Castillo to conform to June 2018 updates.


% Switch this line to the final option when submitting your thesis.
% This will correct counts and remove labels that are shown during draft mode
%\documentclass[masters,draft]{UTRGVthesis}
\documentclass[masters,final]{UTRGVthesis}
%\documentclass[masters,final, nodedication, noacknowledgments]{UTRGVthesis}
%\usepackage{mathpazo}

% Set Custom font, requires XeLaTeX
%\setmainfont{Times New Roman}
%\setmainfont{Comic Sans MS}

% Load your packages below.
% Make hyperref and showkeys come at the end of your loaded packages
% to make sure they are not over-written.  They redefine many
% standard LaTeX commands
\usepackage{docmute} % for inputting complete documents. Useful for LyX users
\usepackage{booktabs} % for better tables
\usepackage{microtype} % for better typography
\usepackage[colorlinks=false]{hyperref}  % for urls
\usepackage{showkeys} % shows labels during draft mode
\usepackage[document]{ragged2e} % uncomment for non-justified text


% Uncomment the line below to check if text is aligned to margins
%\margins

% To change body font from Times Roman to Times New Roman, compile with XeLaTeX
% This assumes you have Times New Roman font installed in your machine
% WARNING! This will NOT change the font in Math Environments
\usepackage{ifxetex}
\ifxetex{}
   \usepackage{fontspec}
   \setmainfont{Times New Roman}
\fi

% This is to ease the use of bibliography from ADS
%  some journals choose to have their name abbreviated with a command
%  assuming the use of the AASTeX package. The following was a file from ADS
%       http://cdsads.u-strasbg.fr/abs_doc/aas_macros.sty
\usepackage{aas_macros}

\usepackage{siunitx} % for proper units

% this sets hanging indention for bibliography
% reference https://tex.stackexchange.com/questions/154622/natbib-will-not-auto-indent-and-bibhang-is-not-recognized
\usepackage[sort&compress,numbers]{natbib}      % for bibliography

\setlength\bibindent{2em}

\makeatletter
\renewcommand\NAT@bibsetnum[1]{\settowidth\labelwidth{\@biblabel{#1}}%
   \setlength{\leftmargin}{\bibindent}\addtolength{\leftmargin}{\dimexpr\labelwidth+\labelsep\relax}%
   \setlength{\itemindent}{-\bibindent}%
   \setlength{\listparindent}{\itemindent}
\setlength{\itemsep}{\bibsep}\setlength{\parsep}{\z@}%
   \ifNAT@openbib
     \addtolength{\leftmargin}{\bibindent}%
     \setlength{\itemindent}{-\bibindent}%
     \setlength{\listparindent}{\itemindent}%
     \setlength{\parsep}{0pt}%
   \fi
}
\makeatother

%\newtotcounter{citesnum} % counter for counting citations
\def\oldcite{} \let\oldcite=\cite
\def\cite{\stepcounter{citesnum}\oldcite}

%\newtotcounter{bibnum} % counter for counting titles in bibliography
\def\oldbibitem{} \let\oldbibitem=\bibitem
\def\bibitem{\stepcounter{bibnum}\oldbibitem}


% this sets the name of the bibliography
% add \vspace{1cm} here to adjust vertical spacing after bibliography title
\renewcommand{\bibname}{BIBLIOGRAPHY}

% Insert your name and major here in the format shown
\Author{Moises Castillo}
\AuthorLastFirst{Castillo, Moises}
\Major{Physics}


% Insert your graduation date here
\Month{August}
\Year{2019}


% Insert the title of your thesis here.
% If you have a long title, split it between multiple lines using the \\ command
% Also, use comment characters to avoid unwanted spaces in the Abstract page
\Title{Pipeline for variable star detection and\\
eclipsing binary characterization}


% Insert your research advisor and his title here
\Advisor{Dr.\ Mario C.\ Diaz}
\AdvisorTitle{Chair of Committee}

% Insert the members of your committee here
% You can also give MemberA a special title
\MemberA{Dr.\ Nicolas Pereyra}  %\MemberATitle{Co-Chair of Committee}
\MemberB{Dr.\ Andreas Hanke}
\MemberC{}
\MemberD{}
\MemberE{}


% Insert the text of your abstract below.
% The bibliography style "citation" required by the manual is automatically
% generated.  Specify the "final" option in the \documentclass to update the
% counts to the correct values.
\Abstract{%
    Stars have been observed and recorded since ancient times.
    Practices of documenting brightness led to observations of variability. 
    Optical CCD observations of eclipsing binary stars were made with instruments
        at UTRGV Dr.\ Cristina Valeria Torres Memorial Astronomical Observatory.
    There are two main goals for this project.
    The first goal is to create a pipeline written in python (lightcurator) that
        creates a framework for detecting variable stars.
    The pipeline starts by creating a list of ccd frames written in FITS format
        of an eclipsing binary star observation.
    These object frames are expected to be already reduced, but lightcurator 
        provides tools to achieve this.
    The object frames are aligned and stacked to create a deepsky frame.
    Astrometry is performed to find the proper positions in right ascension
        and declination of all sources in the deepsky frame.
    This creates a master catalogue of stars to be monitored through the entire observation.
    Source extraction is performed on each object frame to generate a catalogue 
        of stars that includes the measure of instrumental flux and the time recorded.
    After converting instrumental flux to instrumental magnitude, light curves 
        are produced for every object for all frames.
    Currently, lightcurator is limited to detecting cataloged variable stars from the
        General Catalogue of Variable Stars (GCVS) and the Variable Star Index (VSX).
    Identification of the intended eclipsing binary system is confirmed in all cases with this method.
    The second goal for this project is to extract the physical parameters of the eclipsing
        binary systems observed from the time series data computed from the pipeline.
}


% You can dedicate your paper here.  This is optional.
\Dedication{%
    This is dedicated to my mom, Kiryat, and dad, Alfredo.\\
    Gracias por sus consejos, ense\~nansas y todo el amor.
\bigskip
\bigskip

    To my brother, Joe, who supports me no matter what I do.

\bigskip
\bigskip

    To my sister, Kitty, who continues to march foward\\
    to the beat of her own drum.

\bigskip
\bigskip

    To my love, Samantha, for always motivating me to\\
    move foward with what I believe in and for caring for me\\
    no matter how busy you are. I love you.

\bigskip
\bigskip

    To who ever may read this,\\
    may it provide inspiration for you to do great things.

\bigskip

    -Moises
}


% Acknowledge those who helped and supported you here. This is optional.
\Acknowledgments{%
    I would like to acknowledge Mario Claudio Diaz for his continued support
    not only as an academic and research advisor, but a mentor in life.
    Also for entrusting me with the keys of the observatory that 
    allowed this project to exist.
    Richard Camuccio for teaching me what he knows of observatories,
    astronomy, and instrumentation. Also for sharing expeiences that
    helped us grow as academics, researchers, and humans.
    Martin Beroiz for your seemingly infinite wealth of knowledge in
    everything. Your guidance and perspective helped me in classes and
    research. And your work has inspired me to work harder.

    The late Cristina Valeria Torres for her compassion in public
    outreach, teaching, and learning. Her words of advice as a mentor
    and friend have helped me form decisions regarding academia and life.

    The CTMO Team and GAIA for trusting my foward thinking
    and believing, together, we can make our observatory autonomous.
    This allowed me to push this project foward.
    Carlos Colazo, Raul Melia, and Carla Giardini, for teaching me 
    the fundamentals of becoming an observational astronomer through
    practice and many hours of working in the dark.
    The Center for Gravitational Wave Astronomy for financial support.
    Soma Mukherjee, Ivan Davila, and Blanca Garcia for assisting me through
    the administrative requirements to meet the criteria for acceptance.
    Andreas Hanke, Nicolas Pereyra, and Natalia Guevara for agreeing to
    help my thesis process rapidly and unconditionally.
    Pawan Kumar Thapalia for showing me the \LaTeX\ template activley maintained by Guillermo Garza of UTRGV-SMSS\@.

    This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France.  The original description of the VizieR service was
published in A\&AS 143, 23.
    This research made use of ccdproc, an Astropy package for
image reduction (Craig et al. 2017).
}


% Insert your biographical sketch here.
\BiographicalSketch{%
    Moises Castillo, born in Brownsville, Texas and raised in Los Fresnos, Texas.
    Graduated from the pioneering class of the Math and Science Academy
    in 2009.
    Received a Bachelor of Science in Physics in 2012 from UTRGV legacy 
    institution University of Texas at Brownsville.
    Collaborator of the Dr. Cristina Valeria Torres Memorial
    Astronomical Observatory,
    Transient Optical Robotic Observatory of the South. 
    Member of the American Association of Variable Star Observers
     and the American Physical Society.

    Been part of the UTRGV Department of Physics since 2008.
    Worked as lab manager for the physics department from 2009-2014. 
    Developed physics instructional laboratory manuals,
    instructional laboratory apparatuses, and instructional laboratory
    design and storage.
    Developed a physics outreach program with the Society of Physics Students in Brownsville.
Presented physics concepts through large scale demonstrations
to over ten thousand students of the Rio Grande Valley
from McAllen to Santa Rosa to Brownsville and many schools in between.
As an Outdoor Educator, instructed activities such as Canoeing and 
Archery and included physics concepts into all activities taught.
Open to observation and critical feedback.
Academic goal is to get a Ph.D. in Physics to supplement the professional goal for a place in academia.
}



\begin{document}

% This starts page counting in Roman numerals
\frontmatter


% This command makes the formal preliminary pages.
% You can comment it out during the drafting process if you want to save paper.
\makepreliminarypages{}

% These insert a table of contents, list of tables, and list of figures
\tableofcontents
\listoftables
\listoffigures


% This starts regular page counting in Arabic numerals
\mainmatter{}

% This starts double-spaced text.  Opposite command is \singlespacing
\doublespacing{}


% OK. Everything is set up. Insert your thesis below.
% It's a good idea to split your thesis up into different files and use
% the \input command
\input{chapters/introduction.tex}
\input{chapters/eclipsingbinarysystems.tex}
\input{chapters/instrumentation.tex}
\input{chapters/data.tex}

% This makes the bibliography.
% Enter your references in the BibTex file "references.bib"
% You can find bibtex info from Google Scholar.
%\bibliographystyle{siam}
\bibliographystyle{plainnat} % this style shows doi
%\bibliographystyle{plain}
\bibliography{msthesisref}


% Uncomment the \appendix macro below for appendices
% Insert appendix chapters after the macro
%\appendix


% This inserts your Biographical Sketch
\biographypage{}

\end{document}
